The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multi-Phase Forest Inventories

### 2017-09-04 rnw/Introduction.Rnw
update Andreas .4.09.2017(1)

\section{Introdution}
\label{sec:intro}

@@

Despite the broad range of methodological literature and case studies, freely available software supporting the application of the proposed multi-phase sampling methods in forest practice has been rare. Two exceptions are the \proglang{R} package \pkg{JoSAE} by \citet{josae2015} that provides the GREG \citep{sarndal2003} and EBLUP \citep{battese1988} two-phase small area estimator for simple sampling derived under the finite population approach, and the package \pkg{maSAE} by \citet{cullmann2016} who provided an initial implementation of the extended synthetic estimator under two and three-phase sampling \citep{mandallaz2013b, mandallaz2013c}. However, a more comprehensive software package covering a larger variety of sample designs and estimators for forest inventories has not yet been available. Our motivation has been to addressed this lack by the \proglang{R} package \pkg{forestinventory}. The package provides global and small area estimators for two-phase and three-phase forest inventories under simple and cluster sampling, which have been developed under the infinite population approach by Daniel Mandallaz at ETH Zurich between 2008 and 2017. The implemented methods have been demonstrated by case studies in Switzerland \citep{massey2014a, massey2015b, mandallaz2013b} and Germany \citep{hill2017a}. The implemented estimators cover 32 inventory scenarios and can be used for stratification, regression and regression within strata \citep{massey2015}. The long-term objective of \pkg{forestinventory} is to make the broad range of estimators available to a large user community and to facilitate their application in science as well as operational forest management.

The particular objective of this article is to \textbf{a)} establish the link between the mathematical description of the estimators and their implementation in our package, \textbf{b)} illustrate their application to real-world inventory data sets and \textbf{c)} adress special cases and demonstrate how the package-functions handle such situations.

>>>>

\section{Introduction}
\label{sec:intro}

@@

Despite the broad range of methodological literature and case studies, freely available software supporting the application of the well-documented multi-phase sampling methods in forest practice has been rare. Two exceptions are the \proglang{R} package \pkg{JoSAE} by \citet{josae2015} that provides the GREG \citep{sarndal2003} and EBLUP \citep{battese1988} two-phase small area estimator for simple sampling derived under the finite population approach, and the package \pkg{maSAE} by \citet{cullmann2016} who provided an initial implementation of the extended synthetic estimator under two and three-phase sampling \citep{mandallaz2013b, mandallaz2013c}. However, a more comprehensive software package covering a larger variety of sample designs and estimators for forest inventories has not yet been available. Our motivation has been to addressed this lack by the \proglang{R} package \pkg{forestinventory}. The package provides global and small area estimators for two-phase and three-phase forest inventories under simple and cluster sampling, which have been developed under the infinite population approach by Daniel Mandallaz at ETH Zurich between 2008 and 2017. The implemented methods have been demonstrated by case studies in Switzerland \citep{massey2014a, massey2015b, mandallaz2013b} and Germany \citep{hill2017a}. The implemented estimators cover 32 inventory scenarios and can be used for stratification, regression and regression within strata \citep{massey2015}. The long-term objective of \pkg{forestinventory} is to make the broad range of estimators available to a large user community and to facilitate their application in science as well as operational forest management.

The particular objective of this article is to \textbf{a)} establish the link between the mathematical description of the estimators and their implementation in our package, \textbf{b)} illustrate their application to real-world inventory data sets and \textbf{c)} adress special cases and demonstrate how the package-functions handle them.
